---
title: "Infections and antibiotics: ABIS-psoriasis year-3 excluding auto-immune diseases"
author: "Debojyoti Das"
date: "2023-10-09"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

path <- "/Users/debda22/Projects/ingrid_asp_psoriasis_research_center"
output_dir <- paste0(path,"/infection_antibiotic_year_wise/with_overall_freq_imputation_infection_antibiotic_3_year_revision")

dir.create(output_dir, recursive = TRUE)
```

```{r}
pacman::p_load(
  haven,        # File import
  here,         # File locator
  sjlabelled,
  readxl,
  writexl,
  ggplot2,
  janitor,      # 
  data.table,   #
  flextable,    #
  comprehenr,   # List comprehension in R
  tidyverse,    # data management + ggplot2 graphics, 
  stringr,      # manipulate text strings 
  purrr,        # loop over objects in a tidy way
  gtsummary,    # summary statistics and tests 
  broom,        # tidy up results from regressions
  lmtest,       # likelihood-ratio tests
  parameters,   # alternative to tidy up results from regressions
  see,          # alternative to visualize forest plots
  easystats,    # Forest plot
  kableExtra,
  forestploter,
  rempsyc,
  ggpubr,
  lattice,
  naniar,
  VIM,
  mice,          # multivariate
  howManyImputations,
  CALIBERrfimpute,
  miceRanger,
  parallel,
  furrr,
  parameters,
  glmglrt,
  MASS,
  survival,
  MatchIt,
  cobalt,
  marginaleffects,
  officer,
  logistf,
  EValue
  )
```

load helping functions


```{r, include=FALSE}
# helper functions for imputation
src_path <- paste0(path,"/infection_and_antibiotics")
source(paste0(src_path, "/Functions_rmph.R"))
source(paste0(src_path, "/antibiotics_and_infections_helper_functions.R"))
source(paste0(src_path, "/all_parameters_infection_antibiotics_ABIS_year_3.R"))
```

Read cohort data from SAV format file

```{r include=FALSE}
data_path <- paste0(path,"/Linkoping_projects/ABIS_RAW_DATA_SPSS")
abis_table <- read_sav(paste0(data_path, "/ABIS_data_base.sav"))
psoriasis_diagonistic_table <- read_sav(paste0(data_path,"/L40_corrected.sav"))
severity <- readxl::read_excel(paste0(data_path,"/Psoriasis  severity.xlsx"))
```

save ABISnr who participated in year-3
```{r}
participants_ABISnr <- (abis_table %>% dplyr::filter(par_2==1))$ABISnr
```

```{r}
severity <- severity %>%
  dplyr::mutate(
    severity = case_when(
      grepl("sever",`Mild form`,ignore.case = TRUE) ~ "severe",
      grepl("mild",`Mild form`,ignore.case = TRUE) ~ "mild",
      TRUE ~ NA
      )
  ) %>% dplyr::select(ABISnr, severity)      

severe_psoriasis_abis <- (severity %>% dplyr::filter(severity == "severe"))$ABISnr
mild_psoriasis_abis <- (severity %>% dplyr::filter(severity == "mild"))$ABISnr
```

```{r}
i=0
Name <- c()
Label <- c()
for (col in names(abis_table)){
  
  i=i+1
  Name <- c(Name,col)
  
  curr_col_attribute <- attr(abis_table[[col]], "label")
  
  if (is.null(curr_col_attribute)||(length(curr_col_attribute)>1)){
    Label <- c(Label, col)
    } else {
    Label <- c(Label, curr_col_attribute)
    }
} 

abis_table_labels <- data.frame("Name" = Name, "Label" = Label)

psoriasis_diagonistic_table.labels <- 
  to_vec(for (col in names(psoriasis_diagonistic_table)) 
    if(is.null(attr(psoriasis_diagonistic_table[[col]], "label"))) col 
    else attr(psoriasis_diagonistic_table[[col]], "label"))

psoriasis_diagonistic_labels <- 
  data.frame("Name" = names(psoriasis_diagonistic_table), 
             "Label" = psoriasis_diagonistic_table.labels)
```


"""
     Name                                                   Label
1  fr_109 Did the mother have another infection during pregnancy?
2 b_12txt                                   What other infection?
3 c_11txt                                   What other infection?
4  e_9txt                                   What other infection?
5 f_8gtxt                                   What other infection?
"""
```{r}
abis_table_original_infection_txt <- abis_table[,c("ABISnr", "c_11txt")]

abis_table <- abis_table[,c(
  "ABISnr",
  "barn_år_mån", 
  "ageC_2",
  "par_2",  
  "c_10a",
  "c_10b",
  "c_10c",
  "c_10d",
  "c_10e", # meningitis
  "c_10f",
  "c_10g",
  "c_10h",
  "c_10i",
  ########
  "c_10m",
  ########
  "c_11a",
  "c_11b",
  "c_11c",
  "c_11d",
  "c_11e",
  "c_11f",
  # "c_16f",   # Do you think that the child suffers from or is affected by diarrhea 3 times or more / day? 
  # "c_16g",   # Do you think that the child suffers from or is affected by vomiting 3 times or more / day? 
  # "c_26a",   # Has the child been using nasal drops during the period from 12 months old until now? 
  # "c_26b",   # Has the child been using antipyretic medication (Paracetamol) during the period from 12 months old until now?
  # "c_26c",   # Has the child been using antipyretic medication (Acetylsalicylic acid) during the period from 12 months old until now? 
  "c_26d",     # Has the child been using penicillin during the period from 12 months old until now?
  "c_26e",     # Has the child been using other antibiotics, for example Bactrim, Ery-max, Zinacef, Cefamox, during the period from 12 months old until
  "c_26g",     # Has the child been using Cortisone during the period from 12 months old until now?
  # "c_26h",   # Has the child been using cough medicine during the period from 12 months old until now? 
  # "c_35a",   # Has there been an epidemic / contagious disease, with several ill people in the environment of the child? 
  # "c_35b",   # During which period of the childs life (months)? 
  # "c_36",    # Has the child's mother / you been unable to work (on sick leave) due to infection / fever, after the birth of the child?
  # "c_37",    # Has the child's father / you been unable to work (on sick leave) due to infection / fever, after the birth of the child?
  # "c_38",    # Has the child's mother / you suffered from a period (more than 3 days) with diarrhea, after the birth of the child?     
  # "c_39",    # Has the child's father / you suffered from a period (more than 3 days) with diarrhea, after the birth of the child?   
  # "c_40",    # If there are siblings, has anyone of these (since the \"questionnaire-child\" was born) had to stay at home from pre-school / school or been bedbound 
  # "c_41",    # If there are siblings, has anyone of these (since the \"questionnaire-child\" was born) had diarrhea for at least 3 days in a row?
  # "c_42a",     # Has the child had a tonsillectomy?
  # "c_56a",     # Indoor animals when the child was between 1 year and 2.5 years?
  ################### confounders ################################
  ################### psoriasis in family #######################
  "e_34p_1",
  "e_34p_2",
  "e_34p_3",
  "f_28o_1",
  "f_28o_2",
  "f_28o_3",
  "gv_21o1",
  "gv_21o2",
  "gv_21o3",
  ################## confounders ################################
  "Gender", # sex
  "b_5",    # exclusive breast-feeding   
  "fr_12",  # gestation (in weeks)
  "fr_27",  # education mother to minimize missing values we take base education if year-3 data is unavailable
  "fr_28"   # education father
)]

abis_table <- abis_table %>% 
  dplyr::mutate(
    child_dob = as.Date(as.yearmon(as.character(barn_år_mån), format = "%Y%m")),
    infection_frequency = pmax(c_10a,c_10b,c_10c,c_10d,c_10e,
                               c_10f,c_10g,c_10h,c_10i,c_10m, na.rm = TRUE)
    ) %>%
  dplyr::select(-c(c_10e, c_10m))
```

Merge the data to include psoriasis diagonistics

```{r}
psoriasis_data_full <- left_join(abis_table, 
                             psoriasis_diagonistic_table,
                             by = "ABISnr") %>% 
  dplyr::mutate(Diagnos = replace(Diagnos, is.na(Diagnos), "")) %>%
  # reformat the date (of detection)
  dplyr::mutate(
    first_detection = as.Date(as.character(övFörsta), format = "%Y%m%d"), 
    second_detection = as.Date(as.character(övSenaste), format = "%Y%m%d")
    ) %>%
  dplyr::mutate(
    age_first_detection = lubridate::time_length(
      difftime(first_detection,child_dob), "years"),
    age_second_detection = lubridate::time_length(
      difftime(second_detection,child_dob), "years")
  ) %>% mutate_if(is.numeric, round,2)

```

Remove attributes

```{r}
for (col in names(psoriasis_data_full)) {
  for (atr in c("label","label","format.spss", "names", "display_width")){
    if(!(is.null(attr(psoriasis_data_full[[col]], atr)))){
      attr(psoriasis_data_full[[col]], atr) <- NULL
      }
  }   
}

attr(psoriasis_data_full, "notes") <- NULL


for (col in names(psoriasis_data_full)) {
  if(is.labelled(psoriasis_data_full[[col]])){
    
    psoriasis_data_full[col] <- unlabel(psoriasis_data_full[[col]])
    
  }
  
}

psoriasis_data_full <- as.data.frame(psoriasis_data_full)
```

```{r}
psoriasis_data_full <- psoriasis_data_full %>%
  dplyr::mutate(
    composite_psoriasis_heredity = pmin(
      e_34p_1,
      e_34p_2,
      e_34p_3,
      f_28o_1,
      f_28o_2,
      f_28o_3,
      gv_21o1,
      gv_21o2,
      gv_21o3, 
      na.rm = TRUE)
    ) %>% 
  dplyr::mutate(
    first_degree_psoriasis_heredity = ifelse(
      is.na(composite_psoriasis_heredity),0,1)
  ) %>% 
  dplyr::mutate(
  time = ifelse(
    par_2 != 1,
    NA,
    ifelse(is.na(ageC_2),3.00,round(ageC_2/12,2))),
  event =  ifelse(
    par_2 != 1,
    NA,
    ifelse(
      is.na(age_first_detection),
      0,
      ifelse(age_first_detection<=time,1,0)))
) %>%  
  dplyr::select(-c(composite_psoriasis_heredity,
            child_dob,barn_år_mån,
            e_34p_1,e_34p_2,e_34p_3,
            f_28o_1,f_28o_2,f_28o_3,
            gv_21o1,gv_21o2,gv_21o3,
            övAntal,övFörsta,övSenaste,
            first_detection,second_detection,
            par_2, ageC_2
            )
         )
```

convert dichotomous variables to 0/1
```{r}
psoriasis_data_full <- psoriasis_data_full %>%  
  dplyr::mutate(across(                                      
    .cols = all_of(c("Diagnos")),  ## for each column listed and "outcome"
    .fns = ~case_when(                              
      . %in% c("L40")   ~ 1,  ## recode L40 (psoriasis diagnosis) to 1
      . %in% c("") ~ 0,       ## not present  to 0
      TRUE ~ NA_real_)        ## otherwise set to missing
    )
  ) 
  
```

remove cases with other auto immune diseases other than psoriasis

```{r}
print("number of participants with other autoimmune diseases")
print(
  nrow(
    psoriasis_data_full[
      which((
        (psoriasis_data_full$AutoimmDisease == 1)&
          (psoriasis_data_full$Diagnos != 1))),]))

print("number of participants before filtering")
print(nrow(psoriasis_data_full))

print("number of first order heredity psoriasis cases before filtering")
print(psoriasis_data_full %>% 
        dplyr::filter(first_degree_psoriasis_heredity == 1) %>%
        nrow()
      )

psoriasis_data_full <- psoriasis_data_full %>% 
  dplyr::filter(!((AutoimmDisease == 1)&(Diagnos != 1)))

# remove rows with missing sex information
psoriasis_data_full <- psoriasis_data_full %>% dplyr::filter(!is.na(Gender))

print("number of participants after filtering")
print(nrow(psoriasis_data_full))

print("number of first order heredity psoriasis cases after filtering")
print(psoriasis_data_full %>% 
        dplyr::filter(first_degree_psoriasis_heredity == 1) %>%
        nrow()
      )
```
keep only ABISnr that participated

```{r}
print("number of participants before filtering")
print(length(participants_ABISnr))

psoriasis_data_full <- psoriasis_data_full %>%
  dplyr::filter(ABISnr %in% participants_ABISnr)

print("number of participants after filtering")
print(nrow(psoriasis_data_full))

print("number of first order heredity psoriasis cases")
print(psoriasis_data_full %>% 
        dplyr::filter(first_degree_psoriasis_heredity == 1) %>%
        nrow()
      )


print("number of psoriasis cases")
print(psoriasis_data_full %>% 
        dplyr::filter(Diagnos == 1) %>%
        nrow()
      )
```

subset data to include only variables of interest and outcome

```{r}
puberty_age <- 13

lower_age_puberty <- "psoriasis before age 13"
upper_age_puberty <- "psoriasis after age 13"

psoriasis_detection_age_data <- psoriasis_data_full[,c("ABISnr",
                                         "age_first_detection",
                                         "age_second_detection")] %>% 
  dplyr::mutate(age_first_detection_cat = case_when(
    age_first_detection < puberty_age ~ lower_age_puberty,
    age_first_detection >= puberty_age ~ upper_age_puberty, 
    TRUE ~ "Not detected")
    )

```

```{r}
explanatory_vars <- names(psoriasis_data_full)[
  !(names(psoriasis_data_full) %in% 
      c("ABISnr", "Diagnos", 
        "age_first_detection",
        "age_second_detection",
        "AutoimmDisease")
    )
  ]
psoriasis_data_full <- psoriasis_data_full[,c("ABISnr", 
                                              explanatory_vars,
                                              "Diagnos")]


```


custom create variables for different vaccination groups and add to list of variables of interest
```{r}
psoriasis_data_full <- psoriasis_data_full  %>% 
  dplyr::mutate(any_antibiotic = pmax(c_26d,c_26e, na.rm = TRUE)) 


explanatory_vars <- c(explanatory_vars, "any_antibiotic")
```

```{r}
categorical_explanatory_vars <- names(
  psoriasis_data_full)[!(names(psoriasis_data_full) %in% 
                           c("ABISnr",
                             "fr_12",
                             "infection_frequency",
                             "first_degree_psoriasis_heredity",
                             "any_antibiotic", 
                             "Diagnos",
                             "time",
                             "event"))]

```

variable value label correspondence data frame

```{r}
explanatory_vars_df <- data.frame(
  v = character(), 
  v_labels = character(),
  labels = character()
  )


for (col in categorical_explanatory_vars){
   if(col %in% c("time", "event")){
    next
  }
  curr_label <- attr(abis_table[[col]], "labels")
  
  v <-list(col)
  if(!is.null(curr_label)){  
    v_labels <- list(attr(abis_table[[col]], "labels"))
    curr_dt <- data.frame(I(v[[1]]), I(v_labels[[1]]))
    curr_dt[["labels"]] <- rownames(curr_dt)
  } else {
    v_labels <- levels(factor(abis_table[[col]]))
    curr_dt <- data.frame(I(v[[1]]), I(v_labels))
    curr_dt[["labels"]] <- paste0(v_labels," ")
  }
  colnames(curr_dt) <- c("variable", "value", "label")
  
  explanatory_vars_df <- rbind(explanatory_vars_df,curr_dt)
}

rownames(explanatory_vars_df) <- seq(1,dim(explanatory_vars_df)[1])
colnames(explanatory_vars_df) <- c("variable", "value", "label")

```

```{r}
explanatory_vars_df <- explanatory_vars_df %>% 
  rbind(list(variable = rep("infection_frequency",4), value = seq(1,4), 
             label = c("Never","1\u20132 times","3\u20135 times","6 times or more")
             )
        )

explanatory_vars_df <- explanatory_vars_df %>% 
  rbind(list(variable = rep("first_degree_psoriasis_heredity",2), 
             value = seq(0,1), 
             label = c("No", "Yes")
             )
        )

explanatory_vars_df <- explanatory_vars_df %>% 
  rbind(list(variable = rep("any_antibiotic",4), value = seq(1,4), 
             label = c("Never","1\u20132 times","3\u20135 times","6 times or more")
             )
        )

```


answer not given

```{r}
ambiguous_answer <- explanatory_vars_df[((explanatory_vars_df$label %in% c(
              "do not know",
              "Do not know",
              "don't know", 
              "dont know", 
              "don`t know"))),]

for (v in ambiguous_answer$variable) {
  value2replace <- ambiguous_answer[ambiguous_answer$variable == v,]$value
  psoriasis_data_full[[v]][which(psoriasis_data_full[[v]] == value2replace)] <- NA
}
```

```{r}
explanatory_vars_df <- explanatory_vars_df[
  (!(explanatory_vars_df$label %in% c(
    "do not know",
    "Do not know",
    "don't know",
    "dont know",
    "don`t know"))),]

expected_values_df <- explanatory_vars_df %>% 
  group_by(variable) %>%
  summarise(min_val = min(value),max_val = max(value))
```

save original data with missing values factorize variables that are to be treated as categorical before imputation is carried out
```{r}
unfactored_original_psoriasis_data_full <- psoriasis_data_full
```


```{r}
for (cv in unlist(all_parameters$category_variable)){
  
  print(cv)
  curr_parameters <- all_parameters[all_parameters$category_variable == cv,]
  
  psoriasis_data_full <- categorise_variable(psoriasis_data_full,
                          variable2categorise = curr_parameters$variable2categorise[[1]],
                          category_variable = curr_parameters$category_variable[[1]],
                          breaks = curr_parameters$breaks[[1]],
                          labels = curr_parameters$labels[[1]]
)
  psoriasis_data_full[[cv]] <- droplevels(psoriasis_data_full[[cv]])
}


psoriasis_data_full[["Diagnos"]] <- factor(psoriasis_data_full[["Diagnos"]])
```

remove variables that have been recoded to categorical variables

```{r}
psoriasis_data_full <- psoriasis_data_full %>%
  dplyr::select(-all_of(c(categorical_explanatory_vars,"any_antibiotic")))

# rename gestational variable
psoriasis_data_full["Gestational_age"] <- psoriasis_data_full$fr_12
psoriasis_data_full$fr_12 <- NULL
psoriasis_data_full$first_degree_psoriasis_heredity <- NULL
psoriasis_data_full$infection_frequency <- NULL
```

```{r}
psoriasis_data_full <- psoriasis_data_full %>%
  dplyr::select(
    all_of(names(psoriasis_data_full)[c(1,4:ncol(psoriasis_data_full),2,3)])
  )
```

check if factors need re-ordering
```{r}
for (i in seq_along(names(psoriasis_data_full))) {
  voi = names(psoriasis_data_full)[[i]]
  print(paste(i,": ",voi))
  if(is.factor(psoriasis_data_full[[voi]])){
    if(!(voi %in% c("ABISnr", "Diagnos","time", "event"))){
      print(tabyl(psoriasis_data_full, !!sym(voi), Diagnos))
    }
  }
}
```


```{r}
print(names(psoriasis_data_full)[c(11:13,19)])
```

re-order some of the levels
```{r}
for (voi in names(psoriasis_data_full)[c(11:13,19)]) {
   old_levels = levels(psoriasis_data_full[[voi]])
   psoriasis_data_full[[voi]] <- factor(psoriasis_data_full[[voi]],
       levels = rev(old_levels)
   ) 
}

psoriasis_data_full$Cold_12_36_month <- factor(
  psoriasis_data_full$Cold_12_36_month, 
  levels = c("1\u20132 times","3\u20135 times","6 times or more", "Never"))

psoriasis_data_full$Infection_frequency_cat <- factor(
  psoriasis_data_full$Infection_frequency_cat, 
  levels = c("1\u20132 times","3\u20135 times","6 times or more", "Never"))
```

```{r}
# print(psoriasis_data_full %>% tabyl(mumps, Diagnos))
# print(psoriasis_data_full %>% tabyl(rubella, Diagnos))
# print(psoriasis_data_full %>% tabyl(measles, Diagnos))
```

remove factors that have no or very few outcomes to minimize unstable results
```{r}
# psoriasis_data_full <- psoriasis_data_full %>%
#   dplyr::select(-c(Measles, Mumps, Rubella))
```

explore missingness before imputations select possible variables to exclude (with reason)

```{r}
# missingness per variable
P <-sapply(psoriasis_data_full, function(x) mean(is.na(x)))
print("variabels with more than 50% missingness!")
print(names(P[P>0.5]))
```

dropping factors with over 50% missing values 
```{r}
# psoriasis_data_full <- psoriasis_data_full %>% 
#   dplyr::select(-c(tuberculosis_vaccine,other_vaccine,MMR_vaccine))
```

save data compatible for cox-proportional hazard analysis.
Use:

cox_data <- read_sav(paste0(output_dir, "/original_cox_data_year_1.sav"))
cox_data <- cox_data %>%
    mutate(across(where(is.labelled), as_factor))
    
to preserve factors when using later
```{r}
haven::write_sav(data = psoriasis_data_full,
                 path = paste0(output_dir, "/original_cox_data_year_3.sav"))
```

discard time and event columns
```{r}
psoriasis_data_full <- psoriasis_data_full %>%
  dplyr::select(-time,-event)
```

impute missing entries: parallel

```{r}
number_of_imputations <- nimpute(psoriasis_data_full, method = "avg")
print("number of imputations based on mean missingness")
print(number_of_imputations)

n_core = detectCores()
number_imputation_per_core = 2

imp_parallel <- futuremice(
  psoriasis_data_full, 
  m = number_of_imputations,
  parallelseed = 123456,
  n.core = n_core,
  seed = ifelse(n_core == 1,12345, NA),
  use.logical = TRUE,
  n.imp.core = number_imputation_per_core,
  maxit = 0
  )

```

```{r}
pred <- imp_parallel$predictorMatrix

# removes the variable ABISnr from the set of predictors, but still leaves it to be predicted by the other variables.
pred[,"ABISnr"] <- 0
pred[c("Penicillin_12_36_month_dichotomous", "Other_antibiotic_12_36_month_dichotomous"), "Any_antibiotic_cat_dichotomous"] <- 0

pred[c("Cold_12_36_month", 
    "Tonsilitis_12_36_month_dichotomous",
    "Otitis_12_36_month_dichotomous",
    "Pneumonia_12_36_month_dichotomous",
    "Infection_requiring_antibiotic_12_36_month_dichotomous",
    "Gastroenteritis_12_36_month_dichotomous",
    "Influenza_12_36_month_dichotomous",
    "Three_day_fever_12_36_month_dichotomous"), "Infection_frequency_cat"] <- 0


post <- imp_parallel$post

post["Gestational_age"] <-  "imp[[j]][, i] <- squeeze(imp[[j]][, i], c(25, 43))"

```

parallel imputation run

```{r}
start_time <- Sys.time()

imp_parallel <- futuremice(
            psoriasis_data_full, 
            m = number_of_imputations,
            parallelseed = 123456,
            n.core = n_core,
            seed = ifelse(n_core == 1,12345, NA),
            use.logical = TRUE,
            n.imp.core = number_imputation_per_core,
            predictorMatrix = pred,
            post = post,
            maxit = 10,
            progress = TRUE)

end_time <- Sys.time()
print("parallel imputation time")
print(end_time - start_time)
```

impute, then transform
```{r}
long <- mice::complete(imp_parallel, "long", include = TRUE)
long$Streptococcal_infections <- with(long, ifelse((((is.na(
  Otitis_12_36_month_dichotomous
)) &
  (
    is.na(Tonsilitis_12_36_month_dichotomous)
  )) | is.na(Penicillin_12_36_month_dichotomous)
), NA, ifelse(((Otitis_12_36_month_dichotomous == "At least once") &
                 (Penicillin_12_36_month_dichotomous == "At least once")
) |
  ((Tonsilitis_12_36_month_dichotomous == "At least once") &
     (Penicillin_12_36_month_dichotomous == "At least once")
  ), "At least once", "Never")))

long$Streptococcal_infections <- with(long, factor(Streptococcal_infections, levels = c("Never", "At least once")))


long$Influenza_or_other_infection <- with(long, ifelse(
  is.na(Other_infection_12_36_month) &
    is.na(Influenza_12_36_month_dichotomous),
  NA,
  ifelse(((Other_infection_12_36_month ==
             "Yes") | (Influenza_12_36_month_dichotomous == "At least once")
  ), "Yes", "No")
))

long$Influenza_or_other_infection <- with(long, factor(Influenza_or_other_infection, levels = c("No", "Yes")))



long$Respiratory_infections_WCIP <- with(long, ifelse((is.na(Whooping_cough_12_36_month)) &
                                                     (is.na(Cold_12_36_month)) &
                                                     (is.na(Influenza_12_36_month_dichotomous)) &
                                                     (is.na(Pneumonia_12_36_month_dichotomous)),
                                                   NA,
                                                   ifelse(((Whooping_cough_12_36_month == "Yes") |
                                                             (Cold_12_36_month != "Never") |
                                                             (Influenza_12_36_month_dichotomous == "At least once") |
                                                             (Pneumonia_12_36_month_dichotomous == "At least once")
                                                   ), "At least once", "Never")
))

long$Respiratory_infections_WCIP <- with(long, factor(Respiratory_infections_WCIP, levels = c("Never","At least once")))

long$Respiratory_infections_WCP <- with(long, ifelse((is.na(Whooping_cough_12_36_month)) &
                                                     (is.na(Cold_12_36_month)) &
                                                     (is.na(Pneumonia_12_36_month_dichotomous)),
                                                   NA,
                                                   ifelse(((Whooping_cough_12_36_month == "Yes") |
                                                             (Cold_12_36_month != "Never") |
                                                             (Pneumonia_12_36_month_dichotomous == "At least once")
                                                   ), "At least once", "Never")
))

long$Respiratory_infections_WCP <- with(long, factor(Respiratory_infections_WCP, levels = c("Never","At least once")))

long$Other_infections_OCT <- with(long, ifelse((is.na(Other_infection_12_36_month)) &
                                                     (is.na(Chicken_pox)) &
                                                     (is.na(Three_day_fever_12_36_month_dichotomous)),
                                                   NA,
                                                   ifelse(((Other_infection_12_36_month == "Yes") |
                                                             (Chicken_pox == "Yes") |
                                                             (Three_day_fever_12_36_month_dichotomous == "At least once")
                                                   ), "At least once", "Never")
))

long$Other_infections_OCT <- with(long, factor(Other_infections_OCT, levels = c("Never","At least once")))

imp_parallel <- as.mids(long)
```

extract imputed data

```{r}
# extract imputed data

imputed_psoriasis_data_full <- complete(imp_parallel)
original_psoriasis_data_full <- complete(imp_parallel, action = 0)
```

fit univariate logistic regression models using complete-case data

```{r warning=FALSE}
variables2test <- names(original_psoriasis_data_full)[c(3:7,25:26,8:14,27:29,15:24)]

original_cc_univariate_regression_table <- complete_case_univariate_logistic_regression(variables2test, original_psoriasis_data_full)
original_cc_univariate_regression_table <- add_pvalue_correction(original_cc_univariate_regression_table)
```

fit multivariable logistic regression models complete-case data

```{r warning=FALSE}
variables2test <- names(original_psoriasis_data_full)[c(3:7,25:26,8:14,27:29,15:18)]

original_cc_multivariable_regression_table <- complete_case_multivariable_logistic_regression(variables2test, original_psoriasis_data_full)
original_cc_multivariable_regression_table <- add_pvalue_correction(original_cc_multivariable_regression_table)
```

fit univariate logistic regression models and pool parallel imputation data

```{r}
variables2test <- names(imp_parallel$data)[c(3:7,25:26,8:14,27:29,15:24)]

full_imputed_univariate_regression_table <- imputed_univariate_logistic_regression(variables2test, imp_parallel)
full_imputed_univariate_regression_table <- add_pvalue_correction(full_imputed_univariate_regression_table)
```


fit multivariable logistic regression models and pool parallel imputation data

``` {r}
variables2test <- names(imp_parallel$data)[c(3:7,25:26,8:14,27:29,15:18)]

full_imputed_multivariable_regression_table <- imputed_multivariable_logistic_regression(variables2test, imp_parallel)
full_imputed_multivariable_regression_table <- add_pvalue_correction(full_imputed_multivariable_regression_table) 
```

forest plot

```{r}
df2plot <- original_cc_univariate_regression_table %>%
  dplyr::select(term, no, yes, estimate, p.value, conf.low, conf.high, p.bon, p.bh) 

medication_start <- which(
  grepl("^Penicillin",df2plot$term)
  )
first_half = c(1:(medication_start-1))
second_half = c(medication_start:nrow(df2plot))
  
forest_plot <- forest_from_table(
  df2plot = df2plot[first_half,],
  title = "  Year 3 complete-case: univariate regression model",
  univariate = TRUE, imputed_output = FALSE)

filename <-paste(output_dir, "A_cc_univariate_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
# ggsave function
save_forest_plot(forest_plot, filename)

forest_plot <- forest_from_table(
  df2plot = df2plot[second_half,],
  title = "  Year 3 complete-case: univariate regression model",
  univariate = TRUE, imputed_output = FALSE)

filename <-paste(output_dir, "B_cc_univariate_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
# ggsave function
save_forest_plot(forest_plot, filename)
```

```{r}
df2plot <- original_cc_multivariable_regression_table %>% 
  dplyr::select(term, no, yes, estimate, p.value, conf.low, conf.high, p.bon, p.bh)

medication_start <- which(
  grepl("^Penicillin",df2plot$term)
  )
first_half = c(1:(medication_start-1))
second_half = c(medication_start:nrow(df2plot))

forest_plot_A <- forest_from_table(
  df2plot = df2plot[first_half,],
  title = " Year 3 complete-case: multivariable regression model",
  univariate = FALSE, imputed_output = FALSE)

forest_plot_B <- forest_from_table(
  df2plot = df2plot[second_half,],
  title = " Year 3 complete-case: multivariable regression model",
  univariate = FALSE, imputed_output = FALSE)

# ggsave function
filename <-paste(output_dir, "A_cc_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_A, filename)

# ggsave function
filename <-paste(output_dir, "B_cc_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_B, filename)
```


```{r include=FALSE}
df2plot <- full_imputed_univariate_regression_table[-c(5,47:52),] %>%
  dplyr::select(term, no, yes, estimate, p.value, conf.low, conf.high, p.bon, p.bh)

one_half <- half_mark(df2plot)
  
forest_plot <- forest_from_table(
  df2plot = df2plot[c(1:one_half),],
  title = " Year 3 imputed: univariate regression model",
  univariate = TRUE, imputed_output = TRUE)

filename <-paste(output_dir, "A_imp_univariate_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
# ggsave function
save_forest_plot(forest_plot, filename)


forest_plot <- forest_from_table(
  df2plot = df2plot[c((one_half+1):nrow(df2plot)),],
  title = " Year 3 imputed: univariate regression model",
  univariate = TRUE, imputed_output = TRUE)

filename <-paste(output_dir, "B_imp_univariate_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")

# ggsave function
save_forest_plot(forest_plot, filename)
```

```{r include=FALSE}
df2plot <- full_imputed_multivariable_regression_table[-c(5,47:52),] %>%
  dplyr::select(term, no, yes, estimate, p.value, conf.low, conf.high, p.bon, p.bh)

medication_start <- which(
  grepl("^Penicillin",df2plot$term)
  )
first_half = c(1:(medication_start-1))
second_half = c(medication_start:nrow(df2plot))
  
forest_plot_A <- forest_from_table(
  df2plot = df2plot[first_half,],
  title = " Year 3 imputed: multivariable regression model",
  univariate = FALSE, imputed_output = TRUE)

# ggsave function
filename <-paste(output_dir, "A_imp_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_A, filename)

forest_plot_B <- forest_from_table(
  df2plot = df2plot[second_half,],
  title = " Year 3 imputed: multivariable regression model",
  univariate = FALSE, imputed_output = TRUE)

# ggsave function
filename <-paste(output_dir, "B_imp_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_B, filename)
```


confounder matched conditional regression

A. matched on Tonsilitis
```{r}
source(paste0(src_path,"/matched_conditional_regression.R", collapse = ""))

covariates2use <- names(original_psoriasis_data_full)[c(4, 19:24)]
antibiotics <- names(original_psoriasis_data_full)[c(15:17)]

pdf(paste0(output_dir,"/year_3_tonsilitis_matched_love_plots.pdf"))

for (iexposure in seq_along(antibiotics)) {
  exposure = antibiotics[iexposure]
  
  print(exposure)
  
  matching.method = "nearest"
  m <- match_and_balance(
    original_psoriasis_data_full,
    exposure,
    covariates2match = covariates2use,
    matching_method = matching.method
  )
  
  clogit_model_results <- conditional_regression(m[[3]], exposure, matchMethod = "nearest")
  
  clogit_result <- clogit_model_results[[2]]
  
  additional_match <- gsub("_", " ", gsub("_cat", "", gsub(
    "_dichotomous", "", gsub("_12_36_month", "", covariates2use[1])
  )))
  
  clogit_result["Additional.Match"] = c(NA_character_, rep(additional_match , nrow(clogit_result) -
                                                             1))
  
  # 2. Extract balance table (SMDs)
  bal <- bal.tab(m[[2]], un = TRUE)
  bal_df <- as.data.frame(bal$Balance)
  bal_df$Exposure <- exposure
  bal_df$Term <- sapply(rownames(bal_df), function(x) gsub("_", " ", gsub("_cat", "", gsub(
    "_dichotomous", "", gsub("_12_36_month", "", x)))))
  bal_df <- bal_df %>%
    dplyr::mutate(Exposure = ifelse(
      row_number() != 1 &
        lag(Exposure) == Exposure,
      NA_character_,
      gsub("_", " ", gsub(
        "_cat", "", gsub("_dichotomous", "", gsub("_12_36_month", "", Exposure))
      ))
    )) %>%
    dplyr::select(Exposure, Term, Type, Diff.Un, Diff.Adj) 

    # 3. Console summary of SMD improvement
  smd_before <- sum(abs(bal_df$Diff.Un) > 0.1, na.rm = TRUE)
  smd_after  <- sum(abs(bal_df$Diff.Adj) > 0.1, na.rm = TRUE)
  message("  Covariates with SMD > 0.1 before: ", smd_before)
  message("  Covariates with SMD > 0.1 after : ", smd_after)
  
    # 3. Add Love plot to combined PDF

  p <- love.plot(
    m[[2]],
    abs = TRUE,
    thresholds = c(m = .1),
    var.order = "unadjusted",
    colors = c("red", "blue"),
    shapes = c("triangle filled", "circle"), 
    sample.names = c("Original", "Weighted"),
    stars = "raw",
    title = paste("Covariate Balance for", gsub("_", " ", gsub(
      "_cat", "", gsub("_dichotomous", "", gsub("_12_36_month", "", exposure))
    )))
  )
  
  print(p + scale_y_discrete(labels = clean_labs))
  
  if (iexposure == 1) {
    matched_exposure_table <- clogit_result
    balance_tables <- bal_df
  } else {
    matched_exposure_table <- rbind(matched_exposure_table, clogit_result)
    balance_tables <- rbind(balance_tables, bal_df)
  }
  
}

dev.off()

write.csv(balance_tables, paste0(output_dir,"/year_3_tonsilitis_matched_SMDs_before_after.csv"), row.names = FALSE)


flextable::save_as_image(
  matched_exposure_table %>%
    flextable::flextable() %>%
    flextable::autofit() %>%
    flextable::footnote(
      i = 1,
      j = 5,
      value = as_paragraph(
        c(
          "matched covariates (Gestational-age, Sex, Education-mother/father, First-degree-psoriasis-heridity, Exclusive-breastfeeding category)"
        )
      ),
      ref_symbols = c("*"),
      part = "header",
      inline = TRUE
    ) %>%
    flextable::fontsize(
      size = 7,
      part = "footer"
    ),
  paste0(output_dir, "/conditional_regression_tonsilitis_year_3.png"),
  expand = 150
)
```

B. Matched on antibiotic
```{r}
exposure = "Tonsilitis_12_36_month_dichotomous" 
antibiotics <- c(
  "Penicillin_12_36_month_dichotomous",
  "Other_antibiotic_12_36_month_dichotomous",
  "Any_antibiotic_cat_dichotomous"
)

base_confounders <- names(original_psoriasis_data_full)[c(19:24)]

pdf(paste0(output_dir,"/year_3_antibiotics_matched_love_plots.pdf"))

for (iab in seq_along(antibiotics)) {
  
  ab = antibiotics[iab]
  covariates2use <- c(ab,base_confounders)
  
  print(covariates2use)
  
  matching.method = "nearest"
  m <- match_and_balance(
    original_psoriasis_data_full,
    exposure,
    covariates2match = covariates2use,
    matching_method = matching.method
  )
  
  clogit_model_results <- conditional_regression(m[[3]], exposure, matchMethod = "nearest")
  
  clogit_result <- clogit_model_results[[2]]
  
  additional_match <- gsub("_", " ", gsub("_cat", "", gsub(
    "_dichotomous", "", gsub("_12_36_month", "", covariates2use[1])
  )))
  
  clogit_result["Additional.Match"] = c(NA_character_, rep(additional_match , nrow(clogit_result) -
                                                             1))
  
    # 2. Extract balance table (SMDs)
  bal <- bal.tab(m[[2]], un = TRUE)
  bal_df <- as.data.frame(bal$Balance)
  bal_df$Exposure <- exposure
  bal_df$Term <- sapply(rownames(bal_df), function(x) gsub("_", " ", gsub("_cat", "", gsub(
    "_dichotomous", "", gsub("_12_36_month", "", x)))))
  bal_df <- bal_df %>%
    dplyr::mutate(Exposure = ifelse(
      row_number() != 1 &
        lag(Exposure) == Exposure,
      NA_character_,
      gsub("_", " ", gsub(
        "_cat", "", gsub("_dichotomous", "", gsub("_12_36_month", "", Exposure))
      ))
    )) %>%
    dplyr::select(Exposure, Term, Type, Diff.Un, Diff.Adj) 
  
      # 3. Console summary of SMD improvement
  smd_before <- sum(abs(bal_df$Diff.Un) > 0.1, na.rm = TRUE)
  smd_after  <- sum(abs(bal_df$Diff.Adj) > 0.1, na.rm = TRUE)
  message("  Covariates with SMD > 0.1 before: ", smd_before)
  message("  Covariates with SMD > 0.1 after : ", smd_after)
  
   # Add Love plot to combined PDF

  p <- love.plot(
    m[[2]],
    abs = TRUE,
    thresholds = c(m = .1),
    var.order = "unadjusted",
    colors = c("red", "blue"),
    shapes = c("triangle filled", "circle"), 
    sample.names = c("Original", "Weighted"),
    stars = "raw",
    title = paste("Covariate Balance for", gsub("_", " ", gsub(
      "_cat", "", gsub("_dichotomous", "", gsub("_12_36_month", "", exposure))
    )))
  )
  
  print(p + scale_y_discrete(labels = clean_labs))
  
  if (iab == 1) {
    matched_exposure_table2 <- clogit_result
    balance_tables <- bal_df
  } else {
    matched_exposure_table2 <- rbind(matched_exposure_table2, clogit_result)
    balance_tables <- rbind(balance_tables, bal_df)
  }
  
}

dev.off()

write.csv(balance_tables, paste0(output_dir,"/year_3_antibiotics_matched_SMDs_before_after.csv"), row.names = FALSE)


flextable::save_as_image(
  matched_exposure_table2 %>%
    flextable::flextable() %>%
    flextable::autofit() %>%
    flextable::footnote(
      i = 1,
      j = 5,
      value = as_paragraph(
        c(
          "matched covariates (Gestational-age, Sex, Education-mother/father, First-degree-psoriasis-heridity, Exclusive-breastfeeding category)"
        )
      ),
      ref_symbols = c("*"),
      part = "header",
      inline = TRUE,
    ) %>%
    flextable::fontsize(size = 7, part = "footer"),
  paste0(
    output_dir,
    "/conditional_regression_antibiotics_year_3.png"
  ),
  expand = 150
)
```

subgroups: puberty age psoriasis detection data set

```{r}
post_puberty_case_control_abis <- (
  psoriasis_detection_age_data %>% 
    dplyr::filter(age_first_detection_cat %in% c("Not detected",
                                          "psoriasis after age 13")))$ABISnr

pre_puberty_case_control_abis <- (
  psoriasis_detection_age_data %>% 
    dplyr::filter(age_first_detection_cat %in% c("Not detected",
                                          "psoriasis before age 13")))$ABISnr

imp_parallel_post_puberty <- imp_parallel %>% 
  dplyr::filter(ABISnr %in% post_puberty_case_control_abis)

imp_parallel_pre_puberty <- imp_parallel %>% 
  dplyr::filter(ABISnr %in% pre_puberty_case_control_abis)
```

psoriasis cases split for puberty age detection data

```{r}
print("psoriasis cases ")
nrow(original_psoriasis_data_full %>% dplyr::filter(Diagnos == 1))

print(paste("psoriasis cases < ", as.character(puberty_age)))
nrow(imp_parallel_pre_puberty$data %>% dplyr::filter(Diagnos == 1))

print(paste("psoriasis cases > ", as.character(puberty_age)))
nrow(imp_parallel_post_puberty$data %>% dplyr::filter(Diagnos == 1))
```

a. post puberty

```{r}
# extract imputed data

imputed_psoriasis_data_post_puberty <- complete(imp_parallel_post_puberty)
original_psoriasis_data_post_puberty <- complete(imp_parallel_post_puberty, action = 0)
```

fit multivariable logistic regression models complete-case post puberty data
```{r warning=FALSE}
variables2test <- names(original_psoriasis_data_post_puberty)[c(3:7,25:26,8:14,27:29,15:18)]

post_puberty_cc_multivariable_regression_table <- complete_case_multivariable_logistic_regression(variables2test, original_psoriasis_data_post_puberty)
post_puberty_cc_multivariable_regression_table <- add_pvalue_correction(post_puberty_cc_multivariable_regression_table)
```

``` {r}
variables2test <- names(imp_parallel_post_puberty$data)[c(3:7,25:26,8:14,27:29,15:18)]

post_puberty_imputed_multivariable_regression_table <- imputed_multivariable_logistic_regression(variables2test, imp_parallel_post_puberty)
post_puberty_imputed_multivariable_regression_table <- add_pvalue_correction(post_puberty_imputed_multivariable_regression_table)
```


forest plot
```{r}
df2plot <- post_puberty_cc_multivariable_regression_table %>% 
  dplyr::select(term, no, yes, estimate, p.value, conf.low, conf.high, p.bon, p.bh)

medication_start <- which(
  grepl("^Penicillin",df2plot$term)
  )
first_half = c(1:(medication_start-1))
second_half = c(medication_start:nrow(df2plot))

forest_plot_A <- forest_from_table(
  df2plot = df2plot[first_half,],
  title = " Year 3 post puberty complete-case: multivariable regression model",
  univariate = FALSE, imputed_output = FALSE)

filename <-paste(output_dir, "A_post_puberty_cc_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_A, filename)

forest_plot_B <- forest_from_table(
  df2plot = df2plot[second_half,],
  title = " Year 3 post puberty complete-case: multivariable regression model",
  univariate = FALSE, imputed_output = FALSE)

filename <-paste(output_dir, "B_post_puberty_cc_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_B, filename)
```

```{r}
df2plot <- post_puberty_imputed_multivariable_regression_table[-c(5),] %>% 
  dplyr::select(term, no, yes, estimate, p.value, conf.low, conf.high, p.bon, p.bh)

medication_start <- which(
  grepl("^Penicillin",df2plot$term)
  )
first_half = c(1:(medication_start-1))
second_half = c(medication_start:nrow(df2plot))

forest_plot_A <- forest_from_table(
  df2plot = df2plot[first_half,],
  title = " Year 3 post puberty imputed: multivariable regression model",
  univariate = FALSE, imputed_output = TRUE)

# ggsave function
filename <-paste(output_dir, "A_post_puberty_imp_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_A, filename)

forest_plot_B <- forest_from_table(
  df2plot = df2plot[second_half,],
  title = " Year 3 post puberty imputed: multivariable regression model",
  univariate = FALSE, imputed_output = TRUE)

# ggsave function
filename <-paste(output_dir, "B_post_puberty_imp_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_B, filename)
```

b. pre puberty

```{r}
# extract imputed data

imputed_psoriasis_data_pre_puberty <- complete(imp_parallel_pre_puberty)
original_psoriasis_data_pre_puberty <- complete(imp_parallel_pre_puberty, action = 0)
```

fit multivariable logistic regression models complete-case pre puberty data
```{r warning=FALSE}
variables2test <- names(original_psoriasis_data_pre_puberty)[c(3:7,25:26,8:14,27:29,15:18)]

pre_puberty_cc_multivariable_regression_table <- complete_case_multivariable_logistic_regression(variables2test, original_psoriasis_data_pre_puberty)
pre_puberty_cc_multivariable_regression_table <- add_pvalue_correction(pre_puberty_cc_multivariable_regression_table)
```


``` {r}
variables2test <- names(imp_parallel_pre_puberty$data)[c(3:7,25:26,8:14,27:29,15:18)]

pre_puberty_imputed_multivariable_regression_table <- imputed_multivariable_logistic_regression(variables2test, imp_parallel_pre_puberty)
pre_puberty_imputed_multivariable_regression_table <- add_pvalue_correction(pre_puberty_imputed_multivariable_regression_table) 
```


forest plot

```{r}
df2plot <- pre_puberty_cc_multivariable_regression_table %>% 
  dplyr::select(term, no, yes, estimate, p.value, conf.low, conf.high, p.bon, p.bh)

medication_start <- which(
  grepl("^Penicillin",df2plot$term)
  )
first_half = c(1:(medication_start-1))
second_half = c(medication_start:nrow(df2plot))

forest_plot_A <- forest_from_table(
  df2plot = df2plot[first_half,],
  title = " Year 3 pre puberty complete-case: multivariable regression model",
  univariate = FALSE, imputed_output = FALSE)

filename <-paste(output_dir, "A_pre_puberty_cc_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_A, filename)

forest_plot_B <- forest_from_table(
  df2plot = df2plot[second_half,],
  title = " Year 3 pre puberty complete-case: multivariable regression model",
  univariate = FALSE, imputed_output = FALSE)

filename <-paste(output_dir, "B_pre_puberty_cc_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_B, filename)
```


```{r}
df2plot <- pre_puberty_imputed_multivariable_regression_table[-c(5,36:38,46,47:52),] %>%
  dplyr::select(term, no, yes, estimate, p.value, conf.low, conf.high, p.bon, p.bh)

medication_start <- which(
  grepl("^Penicillin",df2plot$term)
  )
first_half = c(1:(medication_start-1))
second_half = c(medication_start:nrow(df2plot))

forest_plot_A <- forest_from_table(
  df2plot = df2plot[first_half,],
  title = " Year 3 pre puberty imputed: multivariable regression model",
  univariate = FALSE, imputed_output = TRUE)

filename <-paste(output_dir, "A_pre_puberty_imp_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_A, filename)

forest_plot_B <- forest_from_table(
  df2plot = df2plot[second_half,],
  title = " Year 3 pre puberty imputed: multivariable regression model",
  univariate = FALSE, imputed_output = TRUE)

filename <-paste(output_dir, "B_pre_puberty_imp_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_B, filename)
```

subgroups: sex specific data

```{r}
boys_case_control_abis <- (unfactored_original_psoriasis_data_full %>% 
    dplyr::filter(Gender == 0))$ABISnr

girls_case_control_abis <- (unfactored_original_psoriasis_data_full %>% 
    dplyr::filter(Gender == 1))$ABISnr

imp_parallel_boys <- imp_parallel %>% 
  dplyr::filter(ABISnr %in% boys_case_control_abis)

imp_parallel_girls <- imp_parallel %>% 
  dplyr::filter(ABISnr %in% girls_case_control_abis)

```

psoriasis cases split for boys and girls specific data

```{r}
print("psoriasis cases ")
nrow(original_psoriasis_data_full %>% dplyr::filter(Diagnos == 1))

print("psoriasis cases in boys")
nrow(imp_parallel_boys$data %>% dplyr::filter(Diagnos == 1))

print("psoriasis cases in girls")
nrow(imp_parallel_girls$data %>% dplyr::filter(Diagnos == 1))

```


a. girls

```{r}
# extract imputed data

imputed_psoriasis_data_girls <- complete(imp_parallel_girls)
original_psoriasis_data_girls <- complete(imp_parallel_girls, action = 0)
```

fit multivariable logistic regression models complete-case girls data
```{r warning=FALSE}
variables2test <- names(original_psoriasis_data_girls)[c(3:7,25:26,8:14,27:29,15:18)]

girls_cc_multivariable_regression_table <- complete_case_multivariable_logistic_regression(variables2test, original_psoriasis_data_girls, sex_specific = TRUE)
girls_cc_multivariable_regression_table <- add_pvalue_correction(girls_cc_multivariable_regression_table)
```


``` {r}
variables2test <- names(imp_parallel_girls$data)[c(3:7,25:26,8:14,27:29,15:18)]

girls_imputed_multivariable_regression_table <- imputed_multivariable_logistic_regression(variables2test, imp_parallel_girls, sex_specific = TRUE)
girls_imputed_multivariable_regression_table <- add_pvalue_correction(girls_imputed_multivariable_regression_table)
```


forest plot

```{r}
df2plot <- girls_cc_multivariable_regression_table %>% 
  dplyr::select(term, no, yes, estimate, p.value, conf.low, conf.high, p.bon, p.bh)

medication_start <- which(
  grepl("^Penicillin",df2plot$term)
  )
first_half = c(1:(medication_start-1))
second_half = c(medication_start:nrow(df2plot))

forest_plot_A <- forest_from_table(
  df2plot = df2plot[first_half,],
  title = " Year 3 girls complete-case: multivariable regression model",
  univariate = FALSE, imputed_output = FALSE)

filename <-paste(output_dir, "A_girls_cc_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_A, filename)

forest_plot_B <- forest_from_table(
  df2plot = df2plot[second_half,],
  title = " Year 3 girls complete-case: multivariable regression model",
  univariate = FALSE, imputed_output = FALSE)

filename <-paste(output_dir, "B_girls_cc_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_B, filename)
```


```{r}
df2plot <- girls_imputed_multivariable_regression_table[-c(5,46, 47:52),] %>%
  dplyr::select(term, no, yes, estimate, p.value, conf.low, conf.high, p.bon, p.bh)

medication_start <- which(
  grepl("^Penicillin",df2plot$term)
  )
first_half = c(1:(medication_start-1))
second_half = c(medication_start:nrow(df2plot))

forest_plot_A <- forest_from_table(
  df2plot = df2plot[first_half,],
  title = " Year 3 girls imputed: multivariable regression model",
  univariate = FALSE, imputed_output = TRUE)

# ggsave function
filename <-paste(output_dir, "A_girls_imp_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_A, filename)

forest_plot_B <- forest_from_table(
  df2plot = df2plot[second_half,],
  title = " Year 3 girls imputed: multivariable regression model",
  univariate = FALSE, imputed_output = TRUE)

# ggsave function
filename <-paste(output_dir, "B_girls_imp_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_B, filename)
```


b. boys

```{r}
# extract imputed data

imputed_psoriasis_data_boys <- complete(imp_parallel_boys)
original_psoriasis_data_boys <- complete(imp_parallel_boys, action = 0)
```

fit multivariable logistic regression models complete-case boys data
```{r warning=FALSE}
variables2test <- names(original_psoriasis_data_boys)[c(3:7,25:26,8:14,27:29,15:18)]

boys_cc_multivariable_regression_table <- complete_case_multivariable_logistic_regression(variables2test, original_psoriasis_data_boys, sex_specific = TRUE)
boys_cc_multivariable_regression_table <- add_pvalue_correction(boys_cc_multivariable_regression_table)
```


``` {r}
variables2test <- names(imp_parallel_boys$data)[c(3:7,25:26,8:14,27:29,15:18)]

boys_imputed_multivariable_regression_table <- imputed_multivariable_logistic_regression(variables2test, imp_parallel_boys, sex_specific = TRUE)
boys_imputed_multivariable_regression_table <- add_pvalue_correction(boys_imputed_multivariable_regression_table) 
```


forest plot

```{r}
df2plot <- boys_cc_multivariable_regression_table %>% 
  dplyr::select(term, no, yes, estimate, p.value, conf.low, conf.high, p.bon, p.bh)

medication_start <- which(
  grepl("^Penicillin",df2plot$term)
  )
first_half = c(1:(medication_start-1))
second_half = c(medication_start:nrow(df2plot))

forest_plot_A <- forest_from_table(
  df2plot = df2plot[first_half,],
  title = " Year 3 boys complete-case: multivariable regression model",
  univariate = FALSE, imputed_output = FALSE)

filename <-paste(output_dir, "A_boys_cc_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_A, filename)

forest_plot_B <- forest_from_table(
  df2plot = df2plot[second_half,],
  title = " Year 3 boys complete-case: multivariable regression model",
  univariate = FALSE, imputed_output = FALSE)

filename <-paste(output_dir, "B_boys_cc_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_B, filename)
```


```{r}
df2plot <- boys_imputed_multivariable_regression_table[-c(5,47:52),] %>%
  dplyr::select(term, no, yes, estimate, p.value, conf.low, conf.high, p.bon, p.bh)

medication_start <- which(
  grepl("^Penicillin",df2plot$term)
  )
first_half = c(1:(medication_start-1))
second_half = c(medication_start:nrow(df2plot))

forest_plot_A <- forest_from_table(
  df2plot = df2plot[first_half,],
  title = " Year 3 boys imputed: multivariable regression model",
  univariate = FALSE, imputed_output = TRUE)


filename <-paste(output_dir, "A_boys_imp_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_A, filename)

forest_plot_B <- forest_from_table(
  df2plot = df2plot[second_half,],
  title = " Year 3 boys imputed: multivariable regression model",
  univariate = FALSE, imputed_output = TRUE)

filename <-paste(output_dir, "B_boys_imp_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_B, filename)
```


```{r}
cases_confirmed <- (imp_parallel$data %>% dplyr::filter(Diagnos == 1))$ABISnr
severity %>% dplyr::filter(!(ABISnr %in% cases_confirmed))

severity <- severity %>% dplyr::filter(ABISnr %in% cases_confirmed)
severity <- severity %>% dplyr::mutate(severity_new=ifelse(is.na(severity),"mild",severity))
```

group by psoriasis disease severity

```{r}
abis_mild <- (severity %>% dplyr::filter(severity_new == "mild"))$ABISnr
abis_severe <- (severity %>% dplyr::filter(severity_new == "severe"))$ABISnr

abis_healthy <- (unfactored_original_psoriasis_data_full %>% 
  dplyr::filter(Diagnos == 0))$ABISnr

mild_case_control_abis <- c(abis_healthy,abis_mild)
severe_case_control_abis <- c(abis_healthy,abis_severe)
```

```{r}
imp_parallel_mild <- imp_parallel %>% 
  dplyr::filter(ABISnr %in% mild_case_control_abis)

imp_parallel_severe <- imp_parallel %>% 
  dplyr::filter(ABISnr %in% severe_case_control_abis)
```

psoriasis cases split for boys and girls specific data

```{r}
print("psoriasis cases ")
nrow(original_psoriasis_data_full %>% dplyr::filter(Diagnos == 1))

print("mild psoriasis cases")
nrow(imp_parallel_mild$data %>% dplyr::filter(Diagnos == 1))

print("severe psoriasis cases")
nrow(imp_parallel_severe$data %>% dplyr::filter(Diagnos == 1))

```


a. severe

```{r}
# extract imputed data

imputed_psoriasis_data_severe <- complete(imp_parallel_severe)
original_psoriasis_data_severe <- complete(imp_parallel_severe, action = 0)
```

fit multivariable logistic regression models complete-case severe data
```{r warning=FALSE}
variables2test <- names(original_psoriasis_data_severe)[c(3:7,25:26,8:14,27:29,15:18)]

severe_cc_multivariable_regression_table <- complete_case_multivariable_logistic_regression(variables2test, original_psoriasis_data_severe)
severe_cc_multivariable_regression_table <- add_pvalue_correction(severe_cc_multivariable_regression_table)
```


``` {r include=FALSE}
variables2test <- names(imp_parallel_severe$data)[c(3:7,25:26,8:14,27:29,15:18)]

severe_imputed_multivariable_regression_table <- imputed_multivariable_logistic_regression(variables2test, imp_parallel_severe)
severe_imputed_multivariable_regression_table <- add_pvalue_correction(severe_imputed_multivariable_regression_table) 
```

forest plot
```{r}
df2plot <- severe_cc_multivariable_regression_table %>% 
  dplyr::select(term, no, yes, estimate, p.value, conf.low, conf.high, p.bon, p.bh)

medication_start <- which(
  grepl("^Penicillin",df2plot$term)
  )
first_half = c(1:(medication_start-1))
second_half = c(medication_start:nrow(df2plot))

forest_plot_A <- forest_from_table(
  df2plot = df2plot[first_half,],
  title = " Year 3 severe complete-case: multivariable regression model",
  univariate = FALSE, imputed_output = FALSE)

filename <-paste(output_dir, "A_severe_cc_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_A, filename)

forest_plot_B <- forest_from_table(
  df2plot = df2plot[second_half,],
  title = " Year 3 severe complete-case: multivariable regression model",
  univariate = FALSE, imputed_output = FALSE)

filename <-paste(output_dir, "B_severe_cc_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_B, filename)
```


```{r}
df2plot <- severe_imputed_multivariable_regression_table[-c(5,36:38,46,47:52),] %>%
  dplyr::select(term, no, yes, estimate, p.value, conf.low, conf.high, p.bon, p.bh)

medication_start <- which(
  grepl("^Penicillin",df2plot$term)
  )
first_half = c(1:(medication_start-1))
second_half = c(medication_start:nrow(df2plot))

forest_plot_A <- forest_from_table(
  df2plot = df2plot[first_half,],
  title = " Year 3 severe imputed: multivariable regression model",
  univariate = FALSE, imputed_output = TRUE)

# ggsave function
filename <-paste(output_dir, "A_severe_imp_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_A, filename)

forest_plot_B <- forest_from_table(
  df2plot = df2plot[second_half,],
  title = " Year 3 severe imputed: multivariable regression model",
  univariate = FALSE, imputed_output = TRUE)

# ggsave function
filename <-paste(output_dir, "B_severe_imp_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_B, filename)
```

b. mild

```{r}
# extract imputed data

imputed_psoriasis_data_mild <- complete(imp_parallel_mild)
original_psoriasis_data_mild <- complete(imp_parallel_mild, action = 0)
```

fit multivariable logistic regression models complete-case mild data
```{r warning=FALSE}
variables2test <- names(original_psoriasis_data_mild)[c(3:7,25:26,8:14,27:29,15:18)]

mild_cc_multivariable_regression_table <- complete_case_multivariable_logistic_regression(variables2test, original_psoriasis_data_mild)
mild_cc_multivariable_regression_table <- add_pvalue_correction(mild_cc_multivariable_regression_table)
```


``` {r}
variables2test <- names(imp_parallel_mild$data)[c(3:7,25:26,8:14,27:29,15:18)]

mild_imputed_multivariable_regression_table <- imputed_multivariable_logistic_regression(variables2test, imp_parallel_mild)
mild_imputed_multivariable_regression_table <- add_pvalue_correction(mild_imputed_multivariable_regression_table) 
```


forest plot
```{r}
df2plot <- mild_cc_multivariable_regression_table %>% 
  dplyr::select(term, no, yes, estimate, p.value, conf.low, conf.high, p.bon, p.bh)

medication_start <- which(
  grepl("^Penicillin",df2plot$term)
  )
first_half = c(1:(medication_start-1))
second_half = c(medication_start:nrow(df2plot))

forest_plot_A <- forest_from_table(
  df2plot = df2plot[first_half,],
  title = " Year 3 mild complete-case: multivariable regression model",
  univariate = FALSE, imputed_output = FALSE)

filename <-paste(output_dir, "A_mild_cc_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_A, filename)

forest_plot_B <- forest_from_table(
  df2plot = df2plot[second_half,],
  title = " Year 3 mild complete-case: multivariable regression model",
  univariate = FALSE, imputed_output = FALSE)

filename <-paste(output_dir, "B_mild_cc_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_B, filename)
```


```{r}
df2plot <- mild_imputed_multivariable_regression_table[-c(5,47:52),] %>%
  dplyr::select(term, no, yes, estimate, p.value, conf.low, conf.high, p.bon, p.bh)

medication_start <- which(
  grepl("^Penicillin",df2plot$term)
  )
first_half = c(1:(medication_start-1))
second_half = c(medication_start:nrow(df2plot))

forest_plot_A <- forest_from_table(
  df2plot = df2plot[first_half,],
  title = " Year 3 mild imputed: multivariable regression model",
  univariate = FALSE, imputed_output = TRUE)

# ggsave function
filename <-paste(output_dir, "A_mild_imp_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_A, filename)

forest_plot_B <- forest_from_table(
  df2plot = df2plot[second_half,],
  title = " Year 3 mild imputed: multivariable regression model",
  univariate = FALSE, imputed_output = TRUE)

# ggsave function
filename <-paste(output_dir, "B_mild_imp_multivariable_forest_plot_infection_antibiotic_year_3.jpeg", sep = "/")
save_forest_plot(forest_plot_B, filename)
```




save all the output tables
```{r}
dataframes2save <- to_vec(for (t in names(which(unlist(eapply(.GlobalEnv,is.data.frame))))) if(grepl("_regression_table",t)) t)

dataframes2save_list <- to_list(for (t in dataframes2save) get(t))

names(dataframes2save_list) <- dataframes2save

filename <-paste(output_dir,"infection_and_antibiotic_year_3.xlsx", sep = "/")
writexl::write_xlsx(dataframes2save_list, path = filename)


# save first imputation instance
filename <-paste(output_dir,"first_imputation_instance_infection_and_antibiotic_year_3.xlsx", sep = "/")
writexl::write_xlsx(imputed_psoriasis_data_full, path = filename)
```



```{r}
psoriasis_detection_age_data_with_inf_txt <- dplyr::full_join(
  psoriasis_detection_age_data,
  abis_table_original_infection_txt,
  by = "ABISnr"
)

original_psoriasis_data_full_with_inf_txt <- dplyr::left_join(
  original_psoriasis_data_full,
  psoriasis_detection_age_data_with_inf_txt,
  by = "ABISnr"
)
```

```{r}
columns2print <- c(
  "ABISnr",
  "Diagnos",
  "severity",
  "c_11txt",
  "age_first_detection",
  "Tonsilitis_12_36_month_dichotomous",
  "Influenza_12_36_month_dichotomous",
  "Streptococcal_infections",
  "Respiratory_infections_WCIP",
  "Respiratory_infections_WCP",
  "Other_infections_OCT",
  "age_first_detection_cat",
  names(original_psoriasis_data_full_with_inf_txt)[!(
    names(original_psoriasis_data_full_with_inf_txt) %in% c(
      "ABISnr",
      "Diagnos",
      "severity",
      "c_11txt",
      "age_first_detection",
      "Tonsilitis_12_36_month_dichotomous",
      "Influenza_12_36_month_dichotomous",
      "Streptococcal_infections",
      "Respiratory_infections_WCIP",
      "Respiratory_infections_WCP",
      "Other_infections_OCT",
      "age_first_detection_cat",
      "age_second_detection"
    )
  )]
)

write.table(
  original_psoriasis_data_full_with_inf_txt %>%
    dplyr::filter(Diagnos == 1) %>%
    dplyr::mutate(
      severity = case_when(
        ABISnr %in% severe_case_control_abis ~ "severe",
        ABISnr %in% mild_case_control_abis ~ "mild",
      )
    ) %>%
    dplyr::select(all_of(columns2print)) %>%
    dplyr::arrange(age_first_detection),
  file = paste0(
    output_dir,
    "/cases_other_infection_detection_age_year_3.csv",
    collapse = ""
  ),
  row.names = FALSE,
  quote = FALSE,
  sep = ","
)
```


onset age association 
```{r}
cases_onset_data <- dplyr::left_join(
  original_psoriasis_data_full, 
  psoriasis_detection_age_data, 
  by = "ABISnr") %>% 
  dplyr::filter(Diagnos==1)

features2test <- names(original_psoriasis_data_full)[
  !(names(original_psoriasis_data_full) %in% 
      c("ABISnr", "Diagnos","Exclusive_breastfeeding_dichotomous_4", 
        "Education_mother", "Education_father", 
        "First_degree_psoriasis_heredity_cat", "Sex_cat", 
        "Gestational_age"))]

mean_age_table_all <- NULL
t_test_table_all <- NULL
wilcox_table_all <- NULL

for(i in seq_along(features2test)){
  
  f <- features2test[[i]] 
    
  data2test <- cases_onset_data %>%
    dplyr::filter(!(is.na(!!sym(f))))
  
  counts <- data2test %>% dplyr::count(!!sym(f))
  
  if(dim(counts %>% dplyr::filter(n>2))[1]==2){
    
    results <- age_of_onset_vs_feature(data2test, f)
    
    mean_age_table <- results[[1]]
    names(mean_age_table)[1] <- "feature"
    mean_age_table <- rbind(data.frame(feature=f, mean_age=NA), mean_age_table)
    
    t_test_table <- results[[2]] %>% dplyr::mutate_if(is.numeric, round,3)
    t_test_table["feature"] <- f
    
    wilcox_table <- results[[3]] %>% dplyr::mutate_if(is.numeric, round,3)
    wilcox_table["feature"] <- f
    
    if(exists("t_test_table_all")){
      mean_age_table_all <- rbind(mean_age_table_all, mean_age_table)
      t_test_table_all <- rbind(t_test_table_all, t_test_table)
      wilcox_table_all <- rbind(wilcox_table_all, wilcox_table)
    } else{
      mean_age_table_all <- mean_age_table
      t_test_table_all <- t_test_table
      wilcox_table_all <- wilcox_table
    }
  
  }
  
}

mean_age_table_all["variable_name"] <- comprehenr::to_vec(
  for(f in mean_age_table_all$feature) 
    if(f %in% c("At least once", "Never", "Yes", "No")) "" else f)

mean_age_table_all$feature <- comprehenr::to_vec(
  for(f in mean_age_table_all$feature) 
    gsub("_"," ",
         gsub("_cat","",
              gsub("_dichotomous","",
                   gsub("_12_36_month","",f)
                   )
              )
         )
  )

t_test_table_all$feature <- comprehenr::to_vec(
  for(f in t_test_table_all$feature) 
    gsub("_"," ",
         gsub("_cat","",
              gsub("_dichotomous","",
                   gsub("_12_36_month","",f)
                   )
              )
         )
  )

wilcox_table_all$feature <- comprehenr::to_vec(
  for(f in wilcox_table_all$feature) 
    gsub("_"," ",
         gsub("_cat","",
              gsub("_dichotomous","",
                   gsub("_12_36_month","",f)
                   )
              )
         )
  )

writexl::write_xlsx(
  x = mean_age_table_all, 
  path = paste0(output_dir, "/mean_onsetage_table_year_3.xlsx")
  )

writexl::write_xlsx(
  x = t_test_table_all, 
  path = paste0(output_dir, "/t_test_onsetage_association_year_3.xlsx")
  )

writexl::write_xlsx(
  x = wilcox_table_all, 
  path = paste0(output_dir, "/wilcox_test_onsetage_association_year_3.xlsx")
  )
```

Firth's Penalized Logistic Regression on original data

original data
```{r}
predictors <- names(original_psoriasis_data_full)[c(3:7,25:26,8:14,27:29,15:18)]
covariates <- names(original_psoriasis_data_full)[c(19:24)]

original_cc_firth_logistic_regression_results <- lapply(predictors, run_firth_logistic, covariates = covariates, data = original_psoriasis_data_full)
original_cc_firth_logistic_regression_table <- do.call(rbind, original_cc_firth_logistic_regression_results)
```

```{r}
flextable_original_cc_firth_logistic_regression_table <- suppressMessages(
  original_cc_firth_logistic_regression_table %>% 
    dplyr::filter(!grepl("Exclusive|Education|Sex|First degree|Gestational",Predictor)) %>% 
    add_evalues()
  ) %>% display_flextable() %>%
  flextable::color(
        i = ~ grepl("Robust", `Remark`),
        j = c(1,2,5),
        color = c("blue", "orange","blue")
  )
```

subsets:
(a) post-puberty cases and controls
```{r}
predictors <- names(original_psoriasis_data_post_puberty)[c(3:7,25:26,8:14,27:29,15:18)]
covariates <- names(original_psoriasis_data_post_puberty)[c(19:24)]

original_cc_post_puberty_firth_logistic_regression_results <- lapply(predictors, run_firth_logistic, covariates = covariates, data = original_psoriasis_data_post_puberty)
original_cc_post_puberty_firth_logistic_regression_table <- do.call(rbind, original_cc_post_puberty_firth_logistic_regression_results)
```

(b) pre-puberty cases and controls
```{r}
predictors <- names(original_psoriasis_data_pre_puberty)[c(3:7,25:26,8:14,27:29,15:18)]
covariates <- names(original_psoriasis_data_pre_puberty)[c(19:24)]

original_cc_pre_puberty_firth_logistic_regression_results <- lapply(predictors, run_firth_logistic, covariates = covariates, data = original_psoriasis_data_pre_puberty)
original_cc_pre_puberty_firth_logistic_regression_table <- do.call(rbind, original_cc_pre_puberty_firth_logistic_regression_results)
```


```{r}
flextable_original_cc_post_puberty_firth_logistic_regression_table <- suppressMessages(
  original_cc_post_puberty_firth_logistic_regression_table %>% 
    dplyr::filter(!grepl("Exclusive|Education|Sex|First degree|Gestational",Predictor)) %>% 
    add_evalues()
  ) %>% display_flextable() %>%
  flextable::color(
        i = ~ grepl("Robust", `Remark`),
        j = c(1,2,5),
        color = c("blue", "orange","blue")
  )

flextable_original_cc_pre_puberty_firth_logistic_regression_table <- suppressMessages(
  original_cc_pre_puberty_firth_logistic_regression_table %>% 
    dplyr::filter(!grepl("Exclusive|Education|Sex|First degree|Gestational",Predictor)) %>% 
    add_evalues()
  ) %>% display_flextable() %>%
  flextable::color(
        i = ~ grepl("Robust", `Remark`),
        j = c(1,2,5),
        color = c("blue", "orange","blue")
  )
```


(c) girls-only data
```{r}
predictors <- names(original_psoriasis_data_girls)[c(3:7,25:26,8:14,27:29,15:18)]
covariates <- names(original_psoriasis_data_girls)[c(19:22,24)]

original_cc_girls_firth_logistic_regression_results <- lapply(predictors, run_firth_logistic, covariates = covariates, data = original_psoriasis_data_girls)
original_cc_girls_firth_logistic_regression_table <- do.call(rbind, original_cc_girls_firth_logistic_regression_results)
```

(d) boys-only data
```{r}
predictors <- names(original_psoriasis_data_boys)[c(3:7,25:26,8:14,27:29,15:18)]
covariates <- names(original_psoriasis_data_boys)[c(19:22,24)]

original_cc_boys_firth_logistic_regression_results <- lapply(predictors, run_firth_logistic, covariates = covariates, data = original_psoriasis_data_boys)
original_cc_boys_firth_logistic_regression_table <- do.call(rbind, original_cc_boys_firth_logistic_regression_results)
```



```{r}
flextable_original_cc_girls_firth_logistic_regression_table <- suppressMessages(
  original_cc_girls_firth_logistic_regression_table %>% 
    dplyr::filter(!grepl("Exclusive|Education|Sex|First degree|Gestational",Predictor)) %>% 
    add_evalues()
  ) %>% display_flextable() %>%
  flextable::color(
        i = ~ grepl("Robust", `Remark`),
        j = c(1,2,5),
        color = c("blue", "orange","blue")
  )

flextable_original_cc_boys_firth_logistic_regression_table <- suppressMessages(
  original_cc_boys_firth_logistic_regression_table %>% 
    dplyr::filter(!grepl("Exclusive|Education|Sex|First degree|Gestational",Predictor)) %>% 
    add_evalues()
  ) %>% display_flextable() %>%
  flextable::color(
        i = ~ grepl("Robust", `Remark`),
        j = c(1,2,5),
        color = c("blue", "orange","blue")
  )
```

(e) mild-cases and controls
```{r}
predictors <- names(original_psoriasis_data_mild)[c(3:7,25:26,8:14,27:29,15:18)]
covariates <- names(original_psoriasis_data_mild)[c(19:24)]

original_cc_mild_firth_logistic_regression_results <- lapply(predictors, run_firth_logistic, covariates = covariates, data = original_psoriasis_data_mild)
original_cc_mild_firth_logistic_regression_table <- do.call(rbind, original_cc_mild_firth_logistic_regression_results)
```

(f) severe-cases and controls
```{r}
predictors <- names(original_psoriasis_data_severe)[c(3:7,25:26,8:14,27:29,15:18)]
covariates <- names(original_psoriasis_data_severe)[c(19:24)]

original_cc_severe_firth_logistic_regression_results <- lapply(predictors, run_firth_logistic, covariates = covariates, data = original_psoriasis_data_severe)
original_cc_severe_firth_logistic_regression_table <- do.call(rbind, original_cc_severe_firth_logistic_regression_results)
```

```{r}
flextable_original_cc_mild_firth_logistic_regression_table <- suppressMessages(
  original_cc_mild_firth_logistic_regression_table %>% 
    dplyr::filter(!grepl("Exclusive|Education|Sex|First degree|Gestational",Predictor)) %>% 
    add_evalues()
  ) %>% display_flextable() %>%
  flextable::color(
        i = ~ grepl("Robust", `Remark`),
        j = c(1,2,5),
        color = c("blue", "orange","blue")
  )

flextable_original_cc_severe_firth_logistic_regression_table <- suppressMessages(
  original_cc_severe_firth_logistic_regression_table %>% 
    dplyr::filter(!grepl("Exclusive|Education|Sex|First degree|Gestational",Predictor)) %>% 
    add_evalues()
  ) %>% display_flextable() %>%
  flextable::color(
        i = ~ grepl("Robust", `Remark`),
        j = c(1,2,5),
        color = c("blue", "orange","blue")
  )
```

```{r}
outdir <- "/Users/debda22/Projects/ingrid_asp_psoriasis_research_center/infection_antibiotic_year_wise/with_overall_freq_imputation_infection_antibiotic_firth_and_evalue_revision"

if(!dir.exists(outdir)){
  dir.create(outdir, recursive = TRUE)
}

```

```{r}
sect_properties <- officer::prop_section(
  page_size = page_size(
    orient = "landscape",
    width = 8.3,
    height = 11.7
  ),
  type = "continuous",
  page_margins = page_mar()
)
```

```{r}
standardize_table <- function(ft, total_width = 8.3) {
  ncols <- ncol(ft$body$dataset)
  
  # Weighting: columns 1,2,5 are wide (weight 2), columns 3,4 are narrow (weight 1)
  weights <- rep(1, ncols)
  weights[c(1, 2, 5)] <- c(4,2,3)
  
  # Normalize to fit total_width
  col_widths <- total_width * (weights / sum(weights))
  
  ft %>%
    autofit() %>% 
    width(j = seq_len(ncols), width = col_widths) %>%
    align(align = "left", part = "all") %>% # consistent alignment
    valign(valign = "center", part = "all") %>%
    flextable::font(fontname = "Times New Roman") %>%  # set font
    flextable::fontsize(size = 10)       
}
```


```{r}
flextable::save_as_docx(
  `Complete-case dataset` = standardize_table(flextable_original_cc_firth_logistic_regression_table),
  `Post-puberty cases and controls dataset` = standardize_table(
    flextable_original_cc_post_puberty_firth_logistic_regression_table
  ),
  `Pre-puberty cases and controls dataset` = standardize_table(
    flextable_original_cc_pre_puberty_firth_logistic_regression_table
  ),
  `Girls-only cases and controls dataset` = standardize_table(
    flextable_original_cc_girls_firth_logistic_regression_table
  ),
  `Boys-only cases and controls dataset` = standardize_table(flextable_original_cc_boys_firth_logistic_regression_table),
  `Mild-cases and controls dataset` = standardize_table(flextable_original_cc_mild_firth_logistic_regression_table),
  `Severe-cases and controls dataset` = standardize_table(
    flextable_original_cc_severe_firth_logistic_regression_table
  ),
  path = paste0(outdir, "/year_3_firth_and_evalue_tables.docx"),
  pr_section = sect_properties
)
```


